Generalized Tractability

### 2023-04-21 GeneralizedTractability_230418.tex
Updates from Overleaf

\fred{Can we say that this notion of tractabilty is stronger or weaker than $\comp(\varepsilon,d)/h(T(\varepsilon^{-1},d,\vp)) \to 0$ as $\varepsilon^{-1} + d \to \infty$?}

@@

\noindent \textbf{Necessary Condition:}\\
Suppose that the problem is  sub-$h \circ T$ tractable. Then, for any $c>0$ there exists a positive integer $V_c$ such that  
\begin{gather*}
	h^{-1}(\comp(\varepsilon,d))\le h^{-1}(\max(1,\comp(\varepsilon,d))) \le cT(\varepsilon^{-1},d)  \qquad \forall \varepsilon^{-1} + d \ge V_c, \\
	\comp(\varepsilon,d) \le \left\lfloor h(cT(\varepsilon^{-1},d)) \right\rfloor \qquad \forall \varepsilon^{-1} + d \ge V_c.
\end{gather*}
By the definition of the information complexity in \eqref{eq:comp_def}, it follows that 
\[
	\lambda_{n(\varepsilon,d,c),d} \le \varepsilon \quad \forall \varepsilon^{-1} + d \ge V_c, \qquad \text{where }
	n(\varepsilon,d,c):=\left\lfloor h(cT(\varepsilon^{-1},d)) \right\rfloor +1.
\]
Since $h(cT(\cdot,d))$ is non-decreasing, it follows that
\begin{equation}
		n(\varepsilon,d,c)\le  h(cT(\varepsilon^{-1},d)) +1\le  h(cT(\lambda^{-1}_{n(\varepsilon,d,c),d},d)) +1\qquad  \quad \forall \varepsilon^{-1} + d \ge V_c. \label{eq:nedcbound}
\end{equation}

>>>>

Note that this definition of sub-$h$-$T$ tractability implies that
\begin{equation} \label{eq:comp_slow_hcT}
		\lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{h(cT(\varepsilon^{-1},d,\vp))} = 0 \qquad \forall c > 0,
\end{equation}
which means that for $\varepsilon \to 0$ or $d \to \infty$  $\comp(\varepsilon,d))$ must increase slower than $h(cT(\varepsilon^{-1},d,\vp))$, no matter how small $c$ is.

@@

\noindent \textbf{Necessary Condition:}\\
Suppose that the problem is  sub-$h \circ T$ tractable. Then by \eqref{eq:comp_slow_hcT}, for any $c>0$ there exists a positive integer $V_c$ such that  
\begin{equation*}
	\comp(\varepsilon,d) \le \left\lfloor h(cT(\varepsilon^{-1},d)) \right\rfloor \qquad \forall \varepsilon^{-1} + d \ge V_c.
\end{equation*}
By the definition of the information complexity in \eqref{eq:comp_def}, it follows that 
\[
	\lambda_{n(\varepsilon,d,c),d} \le \varepsilon \quad \forall \varepsilon^{-1} + d \ge V_c, \qquad \text{where }
	n(\varepsilon,d,c):=\left\lfloor h(cT(\varepsilon^{-1},d)) \right\rfloor +1.
\]
Since $h(cT(\cdot,d))$ is non-decreasing, it follows that
\begin{equation}
		n(\varepsilon,d,c)\le  h(cT(\varepsilon^{-1},d)) +1\le  h(cT(\lambda^{-1}_{n(\varepsilon,d,c),d},d)) +1\qquad  \quad \forall \varepsilon^{-1} + d \ge V_c. \label{eq:nedcbound}
\end{equation}
